Out-of-Sample Comparisons of Overfit Models

### 2014-03-27 paper.tex
Extensive rewrite of the paper's theoretical component
This commit is a major rewrite of the paper's theoretical component,
including both the in-sample and out-of-sample results. The in-sample
proofs still need to be completed, but otherwise this part of the
paper is more or less ready to go.

\begin{asmp}\label{asmp-3}
  The loss function $L$ is continuous, has finite left and right
  derivatives, and $L(0) = 0$.  There is a constant $B_L$ and a
  function $L'$ that bounds the left and right derivative of $L$ at
  every point such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq
  B_L$ for all $t$, where
  \begin{equation*}
    D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
    - L(y^* - x_2^{*\prime}\hat\theta_{2t})
  \end{equation*}
  and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
  distribution but is independent of $\mathcal{F}_T$ ($\rho$ is defined
  in Assumption~\ref{asmp-1}); and
  \begin{equation*}
    \| L'(y^* - x_{i}^{*\prime} (\alpha \bh{iR} + (1-\alpha) \bh{iT})) \|_2
    \leq B_L
  \end{equation*}
  for any $\alpha \in [0,1]$.
\end{asmp}

The differentiability condition in Assumption~\ref{asmp-3} is weak and
allows the loss function itself to be non-differentiable; for example,
absolute error and many asymmetric loss functions satisfy this
assumption. The Assumption makes use of both $(y_{t+\h}, x_{1t},
x_{2t})$ and $(y^*, x_1^*, x_2^*)$ because the period $t$ observations
can be dependent on $\bh{iT}$ in complicated ways. When the underlying
observations are independent these assumptions can simplify
considerably.

The next assumption controls the growth of the test and
training samples.
\begin{asmp} \label{asmp-4} (a) $P, R, Q \to\infty$ as $T \to
  \infty$. (b) $P^2/T \to 0$ as $T \to \infty$.
\end{asmp}

@@

\begin{asmp}
  \label{asmp-5} $W$ is a kernel from
$\Re$ to $[-1,1]$ such that $W(0) = 1$, $W(x) = W(-x)$ for all $x$,
\begin{equation*}
  \int_{-\infty}^{\infty} \lvert W(x) \rvert dx < \infty, \quad
  \int_{-\infty}^{\infty} \lvert \psi(x) \rvert dx < \infty
\end{equation*}
with
\begin{equation*}
  \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
\end{equation*}
and $W(\cdot)$ is continuous at zero and all but a finite number of
points.
\end{asmp}

Assumptions~\ref{asmp-1}--\ref{asmp-5} are broadly similar to
\citepos{Wes:96} assumptions, except with regard to model complexity
and the size of the test sample.  West assumes that $K_1$ and $K_2$
are both finite, while we let them grow rapidly with $T$
(Assumption~\ref{asmp-1}), and West lets $P/R$ converge to any value
in $[0,\infty]$, while we require $P^2/R \to 0$
(Assumption~\ref{asmp-4}).%
\footnote{\citet{Wes:96} does not have a
  second OOS period, so there is no analogue in his paper to our
  restriction on $Q$.} %
Obviously, these differences are
related---allowing for complex models requires tighter constraints on
the size of the test sample.  West allows more general estimation
methods, while we restrict attention to OLS; the advantage of using
OLS is that we can derive the inequality,
\begin{equation*}
  \| x_{it}'\bh{i,T+1} - x_{it}'\bh{iR} \|_2 \leq O(P/T)^{1/2}.
\end{equation*}
Our main results will hold for other models and estimation windows as
long as a similar inequality exists, but proving such inequalities is
left for future research.

Our other assumptions are similar.  The loss function must be smooth
almost everywhere, which is less restrictive than \citet{Wes:96}
requires but is not new; \citet{Mcc:00} extends West's results to
cover a similar case. We assume full stationarity and absolute
regularity of the underlying random array, while West assumes
covariance stationarity and strong mixing of the transformed forecast
errors; and the details our moment conditions are different, but seem
that they would hold in similar environment to West's.  Finally, since
West's is a more standard environment, he assumes the existence of a
consistent estimator of the variance, while we construct it
explicitly.  Only West's assumptions governing model complexity and
the size of the test sample are substantially different than ours.

@@

This section lays out our theoretical results. The first subsection
presents results for the DMW $t$-test; we show that it is
asymptotically normal when one or both forecasting models is overfit.
(i.e., under our increasing-$K$ asymptotic approximation.) We also
present a new limitation on these statistics---OOS comparisons heavily
penalize overfit models unless the size of the test sample is a very
small proportion of the total sample size, which will not be practical
in much applied research. The second subsection presents results for
full-sample statistics and shows that widely used test statistics and
model selection criteria are misleading when choosing a model for
forecasting. In contrast to OOS comparisons, these full-sample
criteria choose overfit models too often, even when they are less
accurate than simple benchmark models. These results are somewhat
abstract, so the third subsection works through an example DGP in
detail.

@@

Instead, we show that $D_t - \E_R D_t$ is an $L_2$-mixingale that
satisfies the CLT. Mixingales satisfy a weak-dependence condition
similar to MDSes,%
\footnote{An array $Z_{n,t}$ and an increasing sequence of \sfields
  $\Gs_{n,t}$ is an \emph{$L_2$-mixingale of size $-1/2$} if there is
  an array of constants $\{c_{n,t}\}$ and a sequence of constants
  $\zeta_l = O(l^{-1/2 - \delta})$ for some $\delta > 0$ such that
  \begin{equation*}
    \lVert \E(Z_{n,t} \mid \Gs_{n,t-l}) \rVert_2
    \leq c_{n,t} \zeta_l
    \qquad\text{and}\qquad
    \lVert Z_{n,t} - \E(Z_{n,t} \mid \Gs_{n,t+l}) \rVert_2
    \leq c_{n,t} \zeta_{l+1}.
  \end{equation*}
  Mixingales were introduced and developed by
  \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.} %
but they have some limitations. Transformations of mixingales are
typically not themselves mixingales, which means that CLTs for
mixingale processes require additional assumptions to hold beyond the
mixingale property.%
\footnote{See \citet{Jon:97} for an illustration. We will borrow
  heavily from his results in our proofs.} %
This is in contrast to Near Epoch Dependent (NED) processes, which
retain the NED property after transformations. \citep[See chapter 17
of][for further discussion of these properties.]{Dav:94} But the OOS
loss has more structure than most mixingales and behaves like an NED
process in important respects.

\begin{lem}\label{res-mixingale}
  If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then $\{D_t - \E_R
  D_t, \mathcal F_t\}$ is an $L_2$-mixingale of size $-1/2$.
  Moreover
  \begin{equation}\label{normalpart}
    \sqrt{P}(\oosA - \E_R \oosA)/\sigma \to^d N(0,1)
  \end{equation}
  as $P \to \infty$ if $\sigma^2$ is uniformly almost surely positive,
  where $\sigma^2 = \var_R(\sqrt{P} \oosA)$ (which is equal to $P
  \E_R(\bar{D}_R - \E_R \bar{D}_R)^2$).
\end{lem}

@@

In our paper, $R$ is not fixed and the forecast errors are not a
convenient weakly-dependent process, since the estimation error in
$\bh{it}$ introduces strong dependence. Consequently,
transformations of the forecast errors are not weakly dependent
either. But this additional dependence has a special form and can be
removed by subtracting the conditional mean; this means that $g(y_{t+\h} -
x_{it}'\bh{it})$ is not weakly dependent but $g(y_{t+\h} -
x_{it}'\bh{it}) - \E_R g(y_{t+\h} - x_{it}'\bh{it})$ is, as long as
the new process satisfies standard moment
restrictions. Assumptions~\ref{asmp-1}--\ref{asmp-3} ensure that these
restrictions are satisfied for $D_t - \E_R D_t$.

The form of the dependence introduced by $\bh{it}$ also allows the CLT
to hold without additional restrictions---the proof rests on showing
that a process like $D_t^2 - \E_R D_t^2$ is also a mixingale, using a
similar argument to the one used by \citet{Jon:97} for NED
processes. This property needs to be established on its own because it
does not follow from the behavior of $D_t - \E_R D_t$.
Lemma~\ref{lem:a2} presents the details of this part of the proof.

@@

\begin{lem} \label{res-convergence}
  Under Assumptions \ref{asmp-1}--\ref{asmp-4}a,
  \begin{equation}\label{eq:7}
    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2} + Q^{-1/2}).
  \end{equation}
  Moreover, there exist processes and loss functions that satisfy
  Assumptions \ref{asmp-1}--\ref{asmp-4}a but $\E_T \oosB - \E_R \oosA
  \neq O_p(1)$ unless $P/T \to 0$.
\end{lem}

We can view $\E_T \oosB - \E_R \oosA$ as noise introduced by
approximating the performance of the full-sample estimates with that
of the partial-sample estimates. The second part of
Lemma~\ref{res-convergence} shows that the $O_p(\sqrt{P/T})$ term
is generally binding; using $\oosA$ to estimate $\E_T \oosB$ requires
$P/T \to 0$ for consistency and using $\sqrt{P} \oosA$ to test
hypotheses about $\E_T \oosB$ requires $P^2/T \to 0$.

Finally, we can use Lemmas~\ref{res-mixingale}
and~\ref{res-convergence} to show that the DMW test is asymptotically
normal and centered at $\E_T \oosB$, as long as
Assumption~\ref{asmp-4}b holds. This theorem justifies using the DMW
$t$-test with a short test sample, which may not be feasible in some
applications.

@@

Finally, we establish that the DMW test can be use to construct
confidence intervals for $\E_T \oosB$ or test hypotheses about $\E_T
\oosB$. In particular, forecasters will often want to test the null
hypothesis that $\E_T \oosB \leq 0$, meaning that the benchmark model
is expected to be more accurate than the alternative model in the
future.

\begin{thm}\label{res:oostest}
  Suppose that the conditions of Theorem
  \ref{res-oost} hold. Then each of the usual Gaussian
  confidence intervals,
  \begin{gather}
    [\oosA - z_{\alpha/2} \, \sh /
    \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
    [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
    \intertext{and}
    (-\infty, \oosA + z_{\alpha} \, \sh / \sqrt{P}],
  \end{gather}
  contains $\E_T\oosB$ with probability $\alpha$ in the limit, with
  $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
  distribution. If $\lim \Pr[\E_T \oosB \leq 0] > 0$ in addition then
  \begin{equation}\label{eq:23}
    \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
    \oosB \leq 0] \leq \alpha.
  \end{equation}
\end{thm}
The results for confidence intervals in Theorem~\ref{res:oostest}
follow immediately from Theorem~\ref{res-oost},
but~\eqref{eq:23} requires additional steps.

@@

In this subsection we look at the behavior of some full-sample
statistics under the same asymptotic theory as before.  We show that
these statistics, which include common tests such as the Wald test as
well as model selection criteria such as the AIC, do not measure the
models' generalization error and consequently do not indicate which
model will be more accurate in the future. Some of these statistics
will tend to choose the larger model regardless of which model will be
more accurate in the future, whereas others tend to choose the smaller
model.  This is a different issue than whether or not full-sample
tests are valid for testing hypotheses about the pseudotrue
coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
demonstrate, variations of the Wald test can be valid for those
hypotheses under increasing-$K$ asymptotics.%
\footnote{\citet{Ana:12} shows that the Wald test is invalid in
  general and gives an adjustment that corrects the critical values;
  he also shows that the $F$-test is asymptotically valid under
  certain conditions on the distribution of the regressors.
  \citet{Cal:11c} shows that the $F$-test is asymptotically invalid
  without Anatolyev's constraint, even under homoskedasticity, and
  provides a correction that gives valid tests.  Both papers only
  consider independent observations.} %
To simplify the presentation we only derive results for nested models
but the conclusions hold more generally.

@@

But for overfit models, the estimates will typically be far from both
their pseudotrue values and from zero. In that case, the Wald test and
the AIC will both tend to choose the larger model even when it is less
accurate than the smaller benchmark model. This phenomenon is driven
by the dimensionality of the alternative model, since there are more
potential values of the coefficient estimator that are far from zero
when it has many elements. The threshold for the Wald test and the AIC
is set by construction to be a bounded distance from the origin.
Every other statistic that shares this property has the same behavior,
since the probability that the coefficient estimators of a
less-accurate but true alternative model fall inside a bounded
threshold are arbitrarily small in the limit. This behavior is
formalized by Theorem~\ref{res:insample1}.
\begin{thm}\label{res:insample1}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold and let
  $\Lambda$ be a model selection statistic that takes the values zero
  or one; $\Lambda = 0$ indicates that the benchmark model is chosen
  and $\Lambda = 1$ indicates the alternative.  Moreover, assume that
  $L(e) = e^2$ and that there exist a deterministic scalar $c$ and a
  sequence of possibly random matrices $V_T$ such that
  \begin{equation}\label{eq:25}
    \Pr[\Lambda > \1\{\bh{2T}' V_T \bh{2T} > c \}] \to 0
    \quad \text{as } T \to \infty
  \end{equation}
  where the eigenvalues of $V_T$ are uniformly bounded in probability
  and $\plim \rank(V_T)/T > 0$.

  Then there exist DGPs satisfing these assumptions such that
  \begin{equation}\label{eq:11}
    \E( \Lambda \mid \E_T \oosB \leq 0 ) \to^p 1.
  \end{equation}
\end{thm}
As we state above,~\eqref{eq:11} means that, with probability
approaching 1, the benchmark model is rejected even when it is more
accurate. The DGPs and statistics used in Theorem~\ref{res:insample1}
are simple and common. The DGPs include correctly specified linear
models with normal and homoskedastic errors. The statistics that meet
the restrictions on $\Lambda$ include the $F$-test and AIC.

For example, the $F$-statistic to test the null that all of the
coefficients unique to the larger model is known to have the form
\begin{equation}\label{eq:17}
  F = \frac{\bh{2T}' M_2' ( M_2 (X_{2T}'X_{2T})^{-1} M_2' )^{-1} M_2
    \bh{2T}}{s^2 (K_2 - K_1)}
\end{equation}
where $s^2$ is the usual estimator of the variance of the regression
error and $M = (0_{K_2 - K_1, K_1}\ \ I_{K_2 - K_1})$. Then let $c$ be any number
greater than 1 and define
\begin{equation*}
  V_T = M_2' \big( M_2 \big(\tfrac{1}{s^2 (K_2 - K_1)} X_{2T}'X_{2T}\big)^{-1}
  M_2' \big)^{-1} M_2'.
\end{equation*}
If Assumption~\ref{asmp-2} holds and $s^2$ is consistent then $V_T$
has uniformly bounded eigenvalues and has rank $K_2 - K_1$, so it
satisfies~\eqref{eq:25}.%
\footnote{If it is surprising that these conditions hold for any $c >
  1$, remember that the $F$ random variable converges to 1 in
  probability as both degrees of freedom diverge to $\infty$ since its
  numerator and denominator both obey the LLN.} %
Robust variations of the Wald test can obviously satisfy~\eqref{eq:25}
for similar reasons, and the AIC for nested linear models is
equivalent to using the $F$-test with the critical value %
$(e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$, %
which converges to a finite limit, so the AIC satisfies~\eqref{eq:25}
as well.

@@

Theorem~\ref{res:insample2} describes this behavior in detail.

\begin{thm}\label{res:insample2}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold, let $L(e) =
  e^2$, and let $\Lambda$ be a model selection statistic as in
  Theorem~\ref{res:insample1}. Also assume that, for any finite scalar
  $c$,
  \begin{equation}\label{eq:27}
    \Pr[\Lambda > \1\{\bh{2T}' V_T \bh{2T} > c \}] \to 1
    \quad \text{as } T \to \infty,
  \end{equation}
  where $V_T$ is a sequence of possibly random matrices with with
  eigenvalues uniformly bounded in probability and $\plim \rank(V_T)/T
  > 0$. Then there exist DGPs satisfing these assumptions such that
  \begin{equation}\label{eq:15}
    \E( \Lambda \mid \E_T \oosB \geq 0 ) \to^p 0.
  \end{equation}
\end{thm}

Again,~\eqref{eq:15} implies that statistics like the BIC will always
choose the smaller model, even when the larger model will give more
accurate forecasts. Both models may be overfit, in that both $K_1/T$
and $K_2/T$ may both be positive in the limit; the key is that $(K_2 -
K_1)/T$ is also positive in the limit.

It is important to remember that, when $\Lambda$ represents a test
statistic, the test may have correct size for the null hypothesis that
the additional coefficients on the larger model are zero. So previous
research, such as \citet{Cal:11c} and \citet{Ana:12}, does not predict
these results. Any statistic that uses the distance of the models'
estimated coefficients from a set point (the origin being the most
common) is poorly suited for choosing between overfit models. These
models only forecast well when their coefficient estimates are close
to their pseudotrue values, which can be far from any prespecified
point. Depending on the statistic, it can be biased towards choosing
the larger model or the smaller model. Formal in-sample tests will
likely be biased towards the larger model, as we show for the $F$-test
in Theorem~\ref{res:insample1}.

\subsection{An extended but simple example}
\label{sec:example}

>>>>

\begin{asmp}\label{asmp-3}
  The loss function $L$ is continuous, has finite left and right
  derivatives, and $L(0) = 0$.  There is a constant $B_L$ and a
  function $L'$ that bounds the left and right derivative of $L$ at
  every point such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq
  B_L$ for all $t$, where
  \begin{equation}
    D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
    - L(y^* - x_2^{*\prime}\hat\theta_{2t})
  \end{equation}
  and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
  distribution but is independent of $\mathcal{F}_T$ ($\rho$ is defined
  in Assumption~\ref{asmp-1}); and
  \begin{equation}\label{eq:29}
    \| L'(y^* - x_{i}^{*\prime} (\alpha \bh{iR} + (1-\alpha) \bh{iT})) \|_2
    \leq B_L
  \end{equation}
  for any $\alpha \in [0,1]$.
\end{asmp}

The differentiability condition in Assumption~\ref{asmp-3} is weak and
allows the loss function itself to be non-differentiable; for example,
absolute error and many asymmetric loss functions satisfy this
assumption. The assumption makes use of both $(y_{t+\h}, x_{1t},
x_{2t})$ and $(y^*, x_1^*, x_2^*)$ because the period $t$ observations
can be dependent on $\bh{iT}$ in complicated ways. When the underlying
observations are independent these assumptions can simplify
considerably.

The next assumption controls the growth of the test and
training samples.
\begin{asmp} \label{asmp-4} (a) $P, R, Q \to\infty$ as $T \to
  \infty$. (b) $P^2/T \to 0$ and $P/Q \to 0$ as $T \to \infty$.
\end{asmp}

@@

\begin{asmp}
  \label{asmp-5} $W$ is a kernel from
$\Re$ to $[-1,1]$ such that $W(0) = 1$, $W(x) = W(-x)$ for all $x$,
\begin{equation}
  \int_{-\infty}^{\infty} \lvert W(x) \rvert dx < \infty, \quad
  \int_{-\infty}^{\infty} \lvert \psi(x) \rvert dx < \infty
\end{equation}
with
\begin{equation}
  \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
\end{equation}
and $W(\cdot)$ is continuous at zero and all but a finite number of
points.
\end{asmp}

These assumptions are broadly similar to those existing in the
literature, with some differences in our assumptions relating the
estimated coefficients to future values of the DGP.
Section~\ref{sec:example} contains an extended example that shows how
these assumptions are satisfied in a simple setting.

@@

This section lays out our theoretical results. The first subsection
presents results for the DMW \oost\ test; we show that it is
asymptotically normal when one or both forecasting models is overfit.
(i.e., under our increasing-$K$ asymptotic approximation.) We also
present a new limitation on these statistics---OOS comparisons heavily
penalize overfit models unless the size of the test sample is a very
small proportion of the total sample size, which will not be practical
in much applied research. The second subsection presents results for
full-sample statistics and shows that widely used test statistics and
model selection criteria are misleading when choosing a model for
forecasting. In contrast to OOS comparisons, these full-sample
criteria choose overfit models too often, even when they are less
accurate than simple benchmark models. These results are somewhat
abstract, so the third subsection works through an example DGP in
detail.

@@

Instead, we show that $D_t - \E_R D_t$ is an $L_2$-mixingale that
satisfies the CLT. Mixingales satisfy a weak-dependence condition
similar to MDSes,%
\footnote{An array $Z_{n,t}$ and an increasing sequence of \sfields
  $\Gs_{n,t}$ is an \emph{$L_2$-mixingale of size $-1/2$} if there is
  an array of constants $\{c_{n,t}\}$ and a sequence of constants
  $\zeta_l = O(l^{-1/2 - \delta})$ for some $\delta > 0$ such that
  \begin{equation*}
    \lVert \E(Z_{n,t} \mid \Gs_{n,t-l}) \rVert_2
    \leq c_{n,t} \zeta_l
    \qquad\text{and}\qquad
    \lVert Z_{n,t} - \E(Z_{n,t} \mid \Gs_{n,t+l}) \rVert_2
    \leq c_{n,t} \zeta_{l+1}.
  \end{equation*}
  Mixingales were introduced and developed by
  \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.} %
but they have some limitations. Transformations of mixingales are
typically not themselves mixingales, which means that CLTs for
mixingale processes require additional assumptions to hold beyond the
mixingale property.%
\footnote{See \citet{Jon:97} for an illustration. We will borrow
  heavily from his results in our proofs.} %
This is in contrast to Near Epoch Dependent (NED) processes, which
retain the NED property after transformations. \citep[See chapter 17
of][for further discussion of these properties.]{Dav:94} But the OOS
loss has more structure than most mixingales and behaves like an NED
process in important respects. (The key result here is
Lemma~\ref{lem:a2} in the Appendix.) Lemma~\ref{res-mixingale} presents the
CLT that we use later, and Section~\ref{sec:example} works through an
i.i.d. example in detail. For i.i.d. observations, the OOS loss is an
MDS and is easier to work with.

\begin{lem}\label{res-mixingale}
  If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then $\{D_t - \E_R
  D_t, \mathcal F_t\}$ is an $L_2$-mixingale of size $-1/2$.
  Moreover
  \begin{equation}
    \sqrt{P}(\oosA - \E_R \oosA)/\sigma \to^d N(0,1)
  \end{equation}
  as $P \to \infty$ if $\sigma^2$ is uniformly almost surely positive,
  where $\sigma^2 = \var_R(\sqrt{P} \oosA)$ (which is equal to $P
  \E_R(\bar{D}_R - \E_R \bar{D}_R)^2$).
\end{lem}

@@

In our paper, $R$ is not fixed and the forecast errors are not a
convenient weakly-dependent process, since the estimation error in
$\bh{it}$ introduces strong dependence. Consequently,
transformations of the forecast errors are not weakly dependent
either. But this additional dependence has a special form and can be
removed by subtracting the conditional mean; specifically $g(y_{t+\h} -
x_{it}'\bh{it})$ is not weakly dependent but $g(y_{t+\h} -
x_{it}'\bh{it}) - \E_R g(y_{t+\h} - x_{it}'\bh{it})$ is.
Assumptions~\ref{asmp-1}--\ref{asmp-3} allow us to show directly
that $D_t - \E_R D_t$ and (crucially) $D^2_t - \E_R D_t^2$ are both
weakly dependent mixingales, ensuring Lemma~\ref{res-mixingale}.

@@

\begin{lem} \label{res-convergence}
  Under Assumptions \ref{asmp-1}--\ref{asmp-4}a,
  \begin{equation}\label{eq:7}
    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2})
    + o_p(Q^{-1/2}).
  \end{equation}
\end{lem}
We can view $\E_T \oosB - \E_R \oosA$ as noise introduced by
approximating the performance of the full-sample estimates with that
of the partial-sample estimates. The key term on the RHS
of~\eqref{eq:7} in practice is $O_p(\sqrt{P/T})$---unless $P/T$ is
small, this noise dominates the OOS average, making it an inconsistent
estimator of $\E_T \oosB$. The $o_p(P^{-1/2})$ term is completely
unrestrictive in our applications because we will multiply the OOS
average by at most $\sqrt{P}$ (for the CLT). And the $o_p(Q^{-1/2})$
term has some implications for interpreting these results: we can only
measure the average performance of the forecasting models for an
extended period in the future, long enough that the future
observations are essentially independent of the current
information. For $Q=1$, for example, the dependence between
$y_{T+\h+1}$ and the current information set $\Fs_T$ may be very
strong.

Finally, we can use Lemmas~\ref{res-mixingale}
and~\ref{res-convergence} to show that the DMW test is asymptotically
normal and centered at $\E_T \oosB$, as long as
Assumption~\ref{asmp-4}b holds. This theorem only establishes the
asymptotic distribution, though.

@@

When $K_1$ and $K_2$ are fixed, West's (1996) and McCracken's (2007)
asymptotic theories apply and the \oost\ test remains normal as long
as $P/T \to 0$, even if $\sigma^2 \to 0$. Under that asymptotic
approximation, the variance will converge to zero whenever the true
DGP is nested in both of the forecasting models. The same principles
may apply in our setting if $K_1$ and $K_2$ grow slowly, so $K_2/T \to
0$. It is likely that a second order expansion along the lines of
\citet{Mcc:07} would lead to asymptotic normality for that
intermediate case, but we leave that issue to future research.

Finally, Theorem~\ref{res:oostest} establishes that the DMW test can be
use to construct confidence intervals for $\E_T \oosB$ and test
hypotheses about $\E_T \oosB$. In particular, forecasters will often
want to test the null hypothesis that $\E_T \oosB \leq 0$, meaning
that the benchmark model is expected to be more accurate than the
alternative model in the future.

\begin{thm}\label{res:oostest}
  Suppose that the conditions of Theorem
  \ref{res-oost} hold. Then each of the usual Gaussian
  confidence intervals,
  \begin{gather}
    [\oosA - z_{\alpha/2} \, \sh /
    \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
    [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
    \intertext{and}
    (-\infty, \oosA + z_{\alpha} \, \sh / \sqrt{P}],
  \end{gather}
  contains $\E_T\oosB$ with probability $\alpha$ in the limit, with
  $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
  distribution. If, in addition, $\lim \Pr[\E_T \oosB \leq 0]$ is
  positive then
  \begin{equation}\label{eq:23}
    \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
    \oosB \leq 0] \leq \alpha.
  \end{equation}
\end{thm}
\noindent
The results for confidence intervals in Theorem~\ref{res:oostest}
follow immediately from Theorem~\ref{res-oost},
but~\eqref{eq:23} requires additional steps.

@@

In this subsection we look at the behavior of some full-sample
statistics under the same asymptotic theory as before.  We show that
these statistics, which include common tests such as the Wald test as
well as model selection criteria such as the AIC, do not measure the
models' generalization error and consequently do not indicate which
model will be more accurate in the future. Some of these statistics
will tend to choose the larger model regardless of which model will be
more accurate in the future, whereas others tend to choose the smaller
model.  This is a different issue than whether or not full-sample
tests are valid for testing hypotheses about the pseudotrue
coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
demonstrate, variations of the Wald test can be valid for those
hypotheses under increasing-$K$ asymptotics.%
\footnote{\citet{Ana:12} shows that the Wald test is invalid in
  general and gives an adjustment that corrects the critical values;
  he also shows that the $F$-test is asymptotically valid under
  certain conditions on the distribution of the regressors.
  \citet{Cal:11c} shows that the $F$-test is asymptotically invalid
  without Anatolyev's constraint, even under homoskedasticity, and
  provides a correction that gives valid tests.  Both papers only
  consider independent observations.} %
To simplify the presentation and the intuition we only derive results
for nested models and for MSE loss, but the conclusions hold much more
generally.%
\footnote{Also, define $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$
  and $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
  selection matrices that return the first $K_1$ and the last $K_2 -
  K_1$ elements of $\theta_2$, and assume that the regressors are
  ordered so that the first $K_1$ elements of $x_{2,t}$ correspond to
  $x_{1,t}$.} %

@@

But for overfit models, the estimates will typically be far from both
their pseudotrue values and also from zero. In that case, the Wald test and
the AIC will both tend to choose the larger model even when it is less
accurate than the smaller benchmark model. This phenomenon is driven
by the dimensionality of the alternative model, since there are more
potential values of the coefficient estimator that are far from zero
when it has many elements. The threshold for the Wald test and the AIC
is set by construction to be a bounded distance from the origin, and
every other statistic that shares this property has the same behavior
and can reject the benchmark model with high probability, even when
it is more accurate. This behavior is
formalized in Theorem~\ref{res:insample1}.

\begin{thm}\label{res:insample1}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold and let
  $\Lambda$ be a model selection statistic that takes the values zero
  or one; $\Lambda = 0$ indicates that the benchmark model is chosen
  and $\Lambda = 1$ indicates the alternative.  Moreover, assume that
  $L(e) = e^2$ and that there exist deterministic scalars $c$ and
  $\delta$ and a sequence of matrices $V_T$ such that
  \begin{equation}\label{eq:25}
    \limsup_{T \to \infty}
    \Pr[\Lambda \geq \1\{\bh{2T}'M_2' V_T M_2\bh{2T} > c \}]
    \leq \delta
  \end{equation}
  where the eigenvalues of $V_T$ are uniformly bounded, and $\lim
  \rank(V_T)/T > 0$.

  Then there exist DGPs satisfying these assumptions such that
  \begin{equation}\label{eq:11}
    \liminf_{T \to \infty} \E( \Lambda \mid \E_T \oosB \leq 0 )
    \to^p \gamma > 1/2 - \delta.
  \end{equation}
\end{thm}

As we state above,~\eqref{eq:11} means that, with high probability,
the benchmark model is rejected even when it is more accurate. In
general, $\delta$ can be made arbitrarily small by increasing the
region enclosed by $\1\{\bh{2T}'M_2' V_T M_2\bh{2T}\}$ and DGPs can be
chosen to put $\gamma$ arbitrarily close to 1 while still satisfying
the assumptions of the Theorem.  The DGPs and
statistics used in Theorem~\ref{res:insample1} are simple and
common. They include correctly specified linear models with normal and
homoskedastic errors; and the statistics that meet the restrictions on
$\Lambda$ include the $F$-test and AIC.

For example, the $F$-statistic to test the null hypothesis that the
benchmark model is correctly specified is known to have the form
\begin{equation*}
  F = \frac{\bh{2T}' M_2' ( M_2 (X_{2T}'X_{2T})^{-1} M_2' )^{-1} M_2
    \bh{2T}}{s^2 (K_2 - K_1)}
\end{equation*}
where $s^2$ is the usual estimator of the variance of the regression
error. Then let $c$ be any number greater than 1 and define
\begin{equation*}
  V_T = M_2' \big( M_2 \big(\tfrac{1}{s^2 (K_2 - K_1)} X_{2T}'X_{2T}\big)^{-1}
  M_2' \big)^{-1} M_2'.
\end{equation*}
If Assumption~\ref{asmp-2} holds and $s^2$ is consistent then $V_T$
has uniformly bounded eigenvalues and has rank $K_2 - K_1$, so it
satisfies~\eqref{eq:25}.%
\footnote{If it is surprising that these conditions hold for any $c >
  1$, remember that the $F$ random variable converges to 1 in
  probability as both degrees of freedom diverge to $\infty$ since its
  numerator and denominator both obey the LLN.} %
Robust variations of the Wald test can obviously satisfy~\eqref{eq:25}
for similar reasons, and the AIC for nested linear models is
equivalent to using the $F$-test with the critical value %
$(e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$, %
which converges to a finite limit, so the AIC satisfies~\eqref{eq:25}
as well.

@@

This behavior is formalized in Theorem~\ref{res:insample2}.
\begin{thm}\label{res:insample2}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold, let $L(e) =
  e^2$, and let $\Lambda$ be a model selection statistic as in
  Theorem~\ref{res:insample1}. Also assume that, for any finite scalar
  $c$,
  \begin{equation}\label{eq:27}
    \Pr[\Lambda \leq \1\{\bh{2T}'M_2' V_T M_2\bh{2T} > c \}] \to 1
    \quad \text{as } T \to \infty,
  \end{equation}
  where $V_T$ is a sequence of deterministic matrices with uniformly
  bounded eigenvalues and $\lim \rank(V_T)/T > 0$. Then there exist
  DGPs satisfying these assumptions such that
  \begin{equation}\label{eq:15}
    \E( \Lambda \mid \E_T \oosB \geq 0 ) \to^p 0.
  \end{equation}
\end{thm}

The condition~\label{eq:27} requires that the acceptance region of
$\Lambda$ eventually contains any finite cylindar centered at the
origin. Again,~\eqref{eq:15} implies that statistics like the BIC
will always choose the smaller model for some DGPs, even when the
larger model will give more accurate forecasts. Both models may be
overfit, in that both $K_1/T$ and $K_2/T$ may both be positive in the
limit; the key is that $(K_2 - K_1)/T$ is also positive in the limit.

It is important to remember that previous research, such as
\citet{Cal:11c} and \citet{Ana:12}, does not predict these
results. When $\Lambda$ represents a test statistic, the test may have
correct size for the null hypothesis that the additional coefficients
on the larger model are zero. The results in this subsection are being
driven by the full-sample statistics' behavior when the smaller model
is misspecified but more accurate.

Any statistic that uses the distance of the models' estimated
coefficients from a set point (the origin being the most common) is
poorly suited for choosing between overfit forecasting models. These
models only forecast well when their coefficient estimates are close
to their pseudotrue values, which can be far from the origin or any
other prespecified
point. Depending on the statistic, it can be biased towards choosing
the larger model or the smaller model. Formal in-sample \emph{tests}
will likely be biased towards the larger model, as we show for the
$F$-test and Wald test in Theorem~\ref{res:insample1}.

\subsection{An extended simple example}
\label{sec:example}
